A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-30 src/tex/ms.tex

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{We manually adjusted the outflow mass-loading parameter $\eta$ and SN Ia yield $y ^{\rm Ia}_{\rm Fe}$ to match the data in the youngest age bin. Key takeaway: the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall. In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall.}
    \label{fig:onezone-dtd}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{{\bf Key takeaway:} the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall. In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall. \todo{Replace APOGEE medians with modes and errors on the mode}}
    \label{fig:onezone-dtd}
\end{figure}
